Projects

### 2024-03-28 qmd/helpful.qmd
added gso page

## R Studio
Great R-Markdown guide made by [Jared Adam](https://www.linkedin.com/in/jared-adam-24b107241/){style="text-decoration: none;"}: 
<a href="https://jared-adam-psu.github.io/R-Tutorial-for-Tooker-Lab/" target="_blank">One code to rule them all (┛ಠ_ಠ)┛彡O</a>

## Quarto Website
YouTube video on how to make a R Studio Quarto Website: [How to create a web site using Quarto, RStudio, and GitHub Pages](https://youtu.be/YN75YXaLFGM?si=RyCG23IMBwFUKsO8)

## GitHub
A great guide to using GitHub created by [Callum Arnold](https://www.linkedin.com/in/arnold-c/){style="text-decoration: none;"}: <a href="https://psu-git.callumarnold.com" target="_blank">Introduction to Git and GitHub</a>

>>>>

## R Studio  
- Guide to using R made by [Jared Adam](https://www.linkedin.com/in/jared-adam-24b107241/){style="text-decoration: none;"}: 
<a href="https://jared-adam-psu.github.io/R-Tutorial-for-Tooker-Lab/" target="_blank">One code to rule them all (┛ಠ_ಠ)┛彡O</a>

## Quarto Website  
- YouTube video on how to make a R Studio Quarto Website: [How to create a web site using Quarto, RStudio, and GitHub Pages](https://youtu.be/YN75YXaLFGM?si=RyCG23IMBwFUKsO8)  
- Gallery showing different options for formatting a Quarto website: [Quarto Gallery](https://quarto.org/docs/gallery/)

## GitHub  
- A guide to using GitHub created by [Callum Arnold](https://www.linkedin.com/in/arnold-c/){style="text-decoration: none;"}: <a href="https://psu-git.callumarnold.com" target="_blank">Introduction to Git and GitHub</a>

### 2024-03-28 qmd/projects.qmd
added gso page

---
title: "Projects"
editor_options: 
  chunk_output_type: console
---

@@

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="projects/msu-masters.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/msu-logo.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Montana State University Master's</h1>
        <p>2021-2024<br> Co-advised by Dr. David Weaver and Dr. Tracy Sterling</p>
      </div>
    </div>
  </a>
  <a href="projects/bballtool.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/bballref-logo-circle.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>NBA Roster Analysis Tool</h1>
        <p>2017-2019</p>
      </div>
    </div>
  </a>
</body>
</html>

>>>>

---
# title: "Projects"
editor_options: 
  chunk_output_type: console
toc: true
---

# Montana State University
<!-- wss -->
<a href="projects/msu-masters/wss.qmd" style="text-decoration:none;">
  <span style="font-size:2em;">Master's Project</span>
</a>
  <span style="fonts-size:1em;">*wheat stem sawfly and native parasitoids*</span>  
<div class="box">  
Understanding the ecological importance of smooth brome (*Bromus inermis*) in biological control of the wheat stem sawfly (*Cephus cinctus*) using native parasitoids. 
<br>  
*PI: [Dr. David Weaver](https://landresources.montana.edu/directory/faculty/1524725/david-weaver){style="text-decoration:none;"}*
</div>
<br>
<!-- locoweed -->
<a href="projects/msu-masters/locoweed.qmd" style="text-decoration:none;">
  <span style="font-size:2em;">Locoweed Volatiles</span>
</a>
  <span style="fonts-size:1em;">*volatile profile differences in Oxytropis sericea*</span>  
<div class="box">  
Measuring the differences in volatile organic compound (VOC) profiles between *Oxytropis sericea* specimens containing the commensal endophyte *Alternaira oxytropos*, and those without.  
<br>
*PI: [Dr. Tracy Sterling](http://weedeco.msu.montana.edu/faculty/tracy_sterling/){style="text-decoration:none;"}*
</div>
<br>
<!-- toadflax -->
<a href="projects/msu-masters/toadflax.qmd" style="text-decoration:none;">
  <span style="font-size:2em;">Toadflax</span>
</a>
  <span style="fonts-size:1em;">*VOC data analysis*</span>  
<div class="box">  
Analyzing the difference in VOC profiles between two toadflax species and hybrids. Project in joint with the US Forest Service. 
<br>  
*PI: [Dr. David Weaver](https://landresources.montana.edu/directory/faculty/1524725/david-weaver){style="text-decoration: none;"} & [Dr. Sharlene Sing (USFS)](https://www.fs.usda.gov/research/about/people/ssing){style="text-decoration:none;"}*
</div>

# Other

<a href="projects/gso.qmd" style="text-decoration:none;">
  <span style="font-size:2em;">LRES Graduate Student Organization</span>
</a>
  <span style="fonts-size:1em;"></span>  
<div class="box">  
Served as the treasurer from 2022-2023, then as co-chair from 2023-2024. Built and managed HTML emails, a website, and organized a research symposium. 
</div>
<br>

<a href="projects/bballtool.qmd" style="text-decoration:none;">
  <span style="font-size:2em;">NBA Roster Analysis Tool</span>
</a>
  <span style="fonts-size:1em;">basketball roster analysis</span>  
<div class="box">  
From 2017 to 2019, I built my own NBA roster analysis tool for analyzing roster construction, free agency, and per-game metrics. The information is out of date, but all of the functionality still works.
</div>

@@

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="projects/msu-masters.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/msu-logo.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Montana State University</h1>
        <p>2021-2024</p>
      </div>
    </div>
  </a>
  <a href="projects/bballtool.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/bballref-logo-circle.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>NBA Roster Analysis Tool</h1>
        <p>2017-2019</p>
      </div>
    </div>
  </a>
</body>
</html>
